---
title: 'TITLE'
author: 'Maria Singstad Paulsen'
date: '`r format(Sys.Date(), "%Y-%B-%d")`'
output:
    pdf_document:
        fig_width: 5
        fig_height: 3.5
        df_print: kable
        highlight: tango
        # default tango pygments kate monochrome espresso zenburn haddock breezedark
    fontsize: 12pt
    # highlight: atelier forest light
    # highlight: solar

    # LaTeX stuff
    # documentclass: scrartcl
    header-includes:
        - \usepackage{amsmath}
        - \usepackage{xcolor}
        - \usepackage{bm}

        # The following lines lets us use the Chancery font with its size altered
        - \DeclareFontFamily{OT1}{pzc}{}
        - \DeclareFontShape{OT1}{pzc}{m}{it}{<->s*[1.2] pzcmi7t}{}
        - \DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
        # - \usepackage[dvipsnames]{xcolor}
---

# Top level headline
## Next level headline (hehehe)

**This is bold text**
*and this is italic text*

### A list is written as follows
* item 1 (`* ' ' text`)
  * item 1.1 (`'  ' * ' ' text`)
    * item 1.1.1 (`'    ' * ' ' text`)
* item 2
  * item 2.1

If we want an inline equation, we use single `$ ... $` like so: $\{x,\,2x,\,|\,x \in \mathbb{N}\}$, and if we want the big ass one, we use the double dollaz `$$ ... $$`. $\LaTeX$ style, in other words. It's also possible to use the newer versions: `\( ... \)` for inline equations and `\[ ... \]` for centered equations. Mixing the two styles is fine as long as consistency between inline and centered equations is kept. I.e., using `$ ... $` and `\[ ... \]`, but sticking to each of them throughout.

$$ \sum_{i=1}^{N}\binom{N}{i}\,,\quad N=10 $$

\[ \sum_{i=1}^{N}\binom{N}{i}\,,\quad N=10 \]

Add extra linespace using the `\medskip` (LaTeX) command:

\medskip


...and even more with the `\bigskip` command:

\bigskip

If we want to continue on a new page, we use the `\newpage` command, like so: \newpage

## R setup code chunk
```{r setup, include = F}
# Initial setup
knitr::opts_chunk$set(echo = TRUE)
# Fix the error "Package xcolor Warning: Incompatible color definition on input line ..."
knitr::knit_hooks$set(document = function(x) {
  sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)
})
```

## Installing packages
```{r, echo = F, warning = F, message = F}
# Uncomment to install various packages.
# install.packages(c('car', 'ggplot2', 'multcomp', 'rlang', 'reticulate'))
# install.packages(c('rms', 'stringi','tidytext', 'tidyverse', 'tm', 'xfun'))
# install.packages(c('topicmodels', 'SnowballC', 'fastmap', 'evaluate'))
# install.packages(c('dplyr', 'corrgram', 'caTools', 'forcats', 'gclus', 'zoo'))
# install.packages(c('iterators', 'gtools', 'gridExtra', 'git2r', 'GGally'))
# install.packages(c('lmtest', 'matrixStats', 'memoise', 'modeltools', 'nlme'))
# install.packages(c('promises', 'progress', 'pkgload', 'pillar', 'nparcomp'))
# install.packages(c('ps', 'purrr', 'quantreg', 'repr', 'reshape2', 'readr'))
# install.packages(c('scales', 'rprojroot', 'rms', 'roxygen2', 'rio', 'rex'))
# install.packages(c('sandwich', 'stringr', 'survival', 'sys', 'testthat'))
# install.packages(c('tidyselect', 'tinytex', 'usethis', 'tidyr', 'tibble'))
# install.packages(c('vcd', 'vctrs', 'viridis', 'visreg', 'xtable', 'yaml'))
```

### Some more or less commonly used packages / libraries
```{r}
library(car) # applied regression stuff
library(corrgram) # plot correlograms, incl. eigenvalue stuff
library(ggplot2) # awesome plots
library(reticulate) # python support
```

### Some libraries relevant to NLP tasks
```{r}
library(tidyverse) # general utility & workflow functions
library(tidytext) # tidy implimentation of NLP methods
# library(topicmodels) # for LDA topic modelling
library(tm) # general text mining functions, making document term matrixes
library(SnowballC) # for stemming
```

## Regular code chunk
```{r, echo = F, warning = F, message = F}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

## Plot code chunk
```{r, echo = T, warning = F, message = F, fig.align = 'center', fig.width = 8, fig.height 6, fig.cap = c('CAPTION_PLOT_1', 'CAPTION_PLOT_2') }
# ... or single plot, meaning only one caption: fig.cap = 'CAPTION'
# plot(something)
```

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to built and preview an output.